---
title: "HTS Households (static)"
author: "Matt Landis"
date: "11/23/2020"
output: 
  html_document:
    code_folding: show
editor_options: 
  chunk_output_type: console
---

```{r setup}

# Set options
knitr::opts_chunk$set(echo = TRUE, comment = '')

suppressPackageStartupMessages({
  library(data.table)
  library(ggplot2)
})


# Load data
hh_labeled = readRDS('data/tnc_bayarea_hh_labeled.rds')
hh_map = hh_labeled[
  !income_aggregate %in% c('Prefer not to answer', 'Missing: Non-response', 'Missing: Skip logic') & !is.na(income_aggregate)]

hh_table = hh_labeled[, .(hh_id, num_people, income_aggregate, rent_own, res_type)]
```


## Including R code

You can include a "chunk" of R code and it will be replaced with the output of the 
code.

```{r show_data}

head(hh_table, 10)

```

## Including Plots

You can also embed plots, for example, here is a simple map of home locations in an HTS survey.

```{r map}

ggplot(hh_map, aes(x=reported_home_lon, y=reported_home_lat)) +
  geom_point(size=2, color='blue', alpha=0.1) +
  coord_equal() +
  labs(x='', y='') +
  theme_bw() 

```

## About

This is a demonstration project to show how to present and interact with household travel survey data.  The project and all source code is available on [Github](https://github.com/landisrm/rTED_2020).

Note: These data have been fully anonymized by randomizing the ids, locations, and descriptive variables.  In addition the actual locations have been jittered.  
