---
title: "Easy interactivity"
author: "Matt Landis"
date: "11/23/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}

# Set options
knitr::opts_chunk$set(echo = TRUE, comment = '')

# Load development version of tmrtools

devtools::load_all('C:/Users/matt.landis/OneDrive - Resource Systems Group, Inc/Git/tmrtools')


# Load libraries 

library(DT)
library(leaflet)

# Load data

data(quakes)

```

## Interactive tables with DT

We can make interactive tables of data very simply, using the [DT](https://rstudio.github.io/DT/) package, which is an R interface to the JavaScript library [DataTables](https://datatables.net/).

```{r quakes}
datatable(quakes)
```

## Interactive maps with leaflet

Making interactive maps is also pretty simple using the [leaflet]() package, which wraps the JavaScript library [Leaflet](https://leafletjs.com/).

This example has been kept simple deliberately for readability.

```{r xyplot}
leaflet(quakes) %>%
  addTiles() %>%
  addCircleMarkers(lng=~long, lat=~lat)
```
